Technical Report

### 2024-03-21 Reports/tech_report1.tex
update Reports
update

\section*{March 6}

@@

	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with coefficient 0.5.

@@

@@

>>>>

\section{March 6}

@@

	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with open ReLU coefficient 0.5.

@@

	\item  However, although the new formula is supposed to be more accurate, the actual result is only a little bit better than old result. This needs to be explained.

@@

\section{March 18}

\subsection*{Gamma of robust 5x100 layer 5}

The output binary file is \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_18_09_23_46.b|. Meanwhile, it try to find the best open number of layer 7.
